Two Mode Networks and Relational Similarity

### 2023-09-08 main.tex

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{Plots/sr-plot.png}
    \caption{Caption}
    \label{fig:simrank}
\end{figure}

@@

And indeed, they are not. Figure~\ref{fig:simrank}(a) and Figure~\ref{fig:simrank}(b) show a plot similar to that shown in Figures~\ref{fig:ca-eigvec}(a) and Figure~\ref{fig:ca-eigvec}(b) but this time with the first non-trivial eigenvector (corresponding to the second-largest eigenvalue) of the SimRank similarity matrices of both persons and groups.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{Plots/sr-plot.png}
    \caption{Caption}
    \label{fig:simrank}
\end{figure}

@@

And indeed, they are not. Figure~\ref{fig:simrank}(a) and Figure~\ref{fig:simrank}(b) show a plot similar to that shown in Figures~\ref{fig:ca-eigvec}(a) and Figure~\ref{fig:ca-eigvec}(b) but this time with the first non-trivial eigenvector (corresponding to the second-largest eigenvalue) of the SimRank similarity matrices of both persons and groups. As we can see, the partitioning of the node sets on the first informative eigenvector is substantively the same, separating the same two blocks of people and events. Figure~\ref{fig:simrank}(c) shows the original affiliation matrix, this time with rows and columns re-arranged according to the main eigenvector of the SimRank similarity matrix. Like in Figure~\ref{fig:ca-v-bon}(a), this reshuffling reveals the block-diagonal structure separating the two blocks of persons and groups. Figure~\ref{fig:simrank}(d) shows the correspondence plot of the first and second informative eigenvector of the SimRank similarity matrices for persons and groups. Once again, this plot is substantively equivalent (in terms of the internode groupings and distances) to that shown in Figure~\ref{fig:ca-sim}(c).
